Contextual Identity: Freedom to be All Your Selves

### 2013-04-23 paper.tex
minor cleanup
Update based on reviews

@@

Those who are aware of having multiple identities engage in the following
techniques to separate, link, and curate identities.

@@

\section{Summary}
People have multiple contextual identities for multiple different reasons. Sharing personal information in
appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and seek to understand identity use better so we can develop tools for effective identity management.

>>>>

Although access control and usability play a role in contextual identity
management, they are not a panacea: many of the below examples fall out of
scope of traditional access control models.

@@

Those who are aware of having multiple identities engage in the following
techniques to separate, link, and curate identities. These techniques are by no
means complete or optimal: people may have latent needs that are not met
by current tools. Studying usage and common problems of these techniques is a
worthy goal.

@@

\section{Summary}
People have multiple contextual identities for many different reasons. Sharing personal information in
appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and seek to understand identity use better so we can develop tools for effective identity management.
